---
title: "horr"
author: "NeoGo"
date: "Monday, May 04, 2015"
output: html_document
---
#Admin's notes
1. Merchandise categories are always very accurate.
2. The bids dataset had some missing data, causing 70 out of the 4700 bidders having 0 bids in the bids dataset.
3. I'm sorry the data description was misleading. This column "Merchandise" is the category of the auction site campaign, which means the bidder might come to this site by way of searching for "home goods" but ended up bidding for "sporting goods" - and that leads to this field being "home goods". This categorical field could be a search term, or online advertisement. This field was aggregated from different sources, but overall it gives you an idea of where the bidder originated from, but not the product itself. And this is the reason that the same auction would have multiple categories. 

#My notes
1. One user may have several friends help him bid a product.
2. Interesting human id : d6517684989560cbb0da1fb2f5bbba9b9y2st
3. Difficult robot id:
1aa0f088fe8934ef831bc5ef06da83e1xl2n4
1a3abce206a20020186d49f835cacfe9gy90h
2cffbc8171f2ef4b5cafe94f038c877bcert5
dee44a87c5db48c9f6ca23e37d6f61074typq
52aaef935c2b3aed6f3ae77bb2bc3513so5h1


#Read in the data
```{r}
Train = read.csv("MyTrain8.csv",stringsAsFactor = FALSE)
Test = read.csv("MyTest7.csv",stringsAsFactor = FALSE)
BadTest = read.csv("BadTest.csv",stringsAsFactor = FALSE)

Train = Train[!(Train$outcome==1 & Train$auc_num==1),] # remove robots with only 1 bid
Train = Train[!(Train$outcome==1 & Train$device_auc_ratio>25),]
Train = Train[!(Train$outcome==0 & Train$auc_num>1000),]

dim(Train)

Train = Train[sample(nrow(Train)),] # if you want to use k-fold cross validation


library(caTools)
spl = sample.split(Train$outcome, SplitRatio = 0.7)
Train_s_train = subset(Train, spl == TRUE) # train of train
Train_s_test = subset(Train, spl == FALSE) # test of train

#BadTest = subset(Test, auc_num == 0)
#BadTest$prediction = 0
#BadTest = select(BadTest, bidder_id, prediction)


bids = read.csv("Bids.csv")
bidssmall = read.csv("bidssmall.csv")
bids = arrange(bids, bidder_id, time, auction)
library(data.table)
library(bit64)
# Read in bids #
bids <- fread(input="MyBids22.csv", header=TRUE)
# Get unique list of bidders and merchandise categories #
merch.cnt.bidder <- bids[, length(unique(merchandise)), by=bidder_id]
setnames(merch.cnt.bidder, c("bidder_id", "merchandise.cnt"))
table(merch.cnt.bidder$merchandise.cnt)
# Get unique list of auctions and merchandise categories #
merch.cnt.auction <- bids[, length(unique(merchandise)), by=auction]
setnames(merch.cnt.auction, c("auction", "merchandise.cnt"))
table(merch.cnt.auction$merchandise.cnt)
```

```{r}
library(tm)
corpus = Corpus(VectorSource(bids$ip))
#corpus = tm_map(corpus, tolower)
corpus = tm_map(corpus, PlainTextDocument)
#corpus = tm_map(corpus, removePunctuation)
#corpus = tm_map(corpus, removeWords, stopwords("english"))
#corpus = tm_map(corpus, stemDocument)
frequencies = DocumentTermMatrix(corpus)
sparse = removeSparseTerms(frequencies, 0.98)
NewsSparse = as.data.frame(as.matrix(sparse))
colnames(NewsSparse) = make.names(colnames(NewsSparse))
```

#Handle the bad data
Removed 29 observation in the Training set without infomation.

#Exploratory Analysis
Train contains (2013 - 29) observations, 4 variables.
Test contains (4700 - 70) observations, 3 variables.
bids contains 7656334 observations, 9 variables.
```{r}
str(Train)
str(Test)
head(Train)
head(Test)
str(bidssmall)
head(bidssmall)
length(unique(bids$time)) # result: 776529
length(unique(bids$bidder_id)) # result: 6614
length(unique(bids$url)) # result: 1786351
length(unique(bids$device)) # result: 7351

length(unique(Train$bidder_id)) # result: 2013
length(unique(Test$bidder_id)) # result: 4700
names(bidssmall)

bids[bids$bidder_id == "9434778d2268f1fa2a8ede48c0cd05c097zey",] # Robot
bids[bids$bidder_id == "e98d8f348b266653b6784329782fd2e91vu3h",] # Human

```

#Data Wrangling
```{r}

#number of payment account this id has
Train$pay_num = 0 
Test$pay_num = 0
for (i in 1:length(Train$payment_account)){
        for (j in 1:length(Train$payment_account)){
                if (Train$payment_account[j] == Train$payment_account[i]){
                        Train$pay_num[i] = Train$pay_num[i] + 1
                }
        }
}
#All of them are paying with one account
Train$pay_num = NULL
Test$pay_num = NULL



#number of address this id has
Train$address_num = 0
for (i in 1:length(Train$address)){
        for (j in 1:length(Train$address)){
                if (Train$address[j] == Train$address[i]){
                        Train$address_num[i] = Train$address_num[i] + 1
                }
        }
}
#All of them are using unique addresses, no repeated addresses

#find number of auctions participated
Train$auc_num = NA
Test$auc_num = NA

#find the number of country in
Train$country_num = NA
Test$country_num = NA

#find the number of device used
Train$device_num = NA
Test$device_num = NA


#find the number of ip only consider the former part
#e.g.: 192.168.1.1, only consider 192.168.
Train$ip_num = NA
Test$ip_num = NA
library(stringr)
bids$ip_ab = str_extract(bids$ip,"\\d+.\\d+")

#find maximum number of bids made over a mechandise
Train$maxnum_b_a_m = NA
Test$maxnum_b_a_m = NA

#find median number of bids of a bidder over mechandises
Train$median_b_a_m = NA
Test$median_b_a_m = NA


#find the number of different kinds of goods bidding for
Train$merchandise_num = NA
Test$merchandise_num = NA

#find the total number of bids made
Train$total_bids_num = NA
Test$total_bids_num = NA




library(dplyr)
for (id in Train$bidder_id){
        #tmp_df = subset(bids, bids$bidder_id == id) # df for this bidder                
        tmp_df = filter(bids, bidder_id == id) # df for this bidder
        Train$total_bids_num[Train$bidder_id == id] = dim(tmp_df)[1]
        Train$country_num[Train$bidder_id == id] = length(unique(tmp_df$country))
        Train$ip_num[Train$bidder_id == id] = length(unique(tmp_df$ip_ab))
        Train$merchandise_num[Train$bidder_id == id] = length(unique(tmp_df$merchandise))
        Train$auc_num[Train$bidder_id == id] = length(unique(tmp_df$auction))
        Train$device_num[Train$bidder_id == id] = length(unique(tmp_df$device))
        Train$maxnum_b_a_m[Train$bidder_id == id] = as.numeric(sort(table(tmp_df$auction),
                                                                    decreasing = TRUE)[1])
        Train$median_b_a_m[Train$bidder_id == id] = median(head(sort(table(tmp_df$auction),
                                                                     decreasing = TRUE)))
        
        
}

for (id in Test$bidder_id){
        #tmp_df_test = subset(bids, bids$bidder_id == id) # df for this bidder
        tmp_df_test = filter(bids, bidder_id == id) # df for this bidder
        Test$total_bids_num[Test$bidder_id == id] = dim(tmp_df_test)[1]
        Test$country_num[Test$bidder_id == id] = length(unique(tmp_df_test$country))
        Test$ip_num[Test$bidder_id == id] = length(unique(tmp_df_test$ip_ab))
        Test$merchandise_num[Test$bidder_id == id] = length(unique(tmp_df_test$merchandise))
        Test$auc_num[Test$bidder_id == id] = length(unique(tmp_df_test$auction))
        Test$device_num[Test$bidder_id == id] = length(unique(tmp_df_test$device))
        Test$maxnum_b_a_m[Test$bidder_id == id] = as.numeric(sort(table(tmp_df_test$auction),
                                                                    decreasing = TRUE)[1])
        Test$median_b_a_m[Test$bidder_id == id] = median(head(sort(table(tmp_df_test$auction),
                                                                     decreasing = TRUE)))
}


# Ratios
Train = mutate(Train, total_auc_ratio = total_bids_num/auc_num)
Test = mutate(Test, total_auc_ratio = total_bids_num/auc_num)

Train = mutate(Train, max_median_prdt = median_b_a_m * maxnum_b_a_m) 
Test = mutate(Test, max_median_prdt = median_b_a_m * maxnum_b_a_m)

Train = mutate(Train, success_auc_ratio = success_bid_num/auc_num)
Test = mutate(Test, success_auc_ratio = success_bid_num/auc_num)

Train = mutate(Train, success2_auc_ratio = success_bid_num^2/auc_num)
Test = mutate(Test, success2_auc_ratio = success_bid_num^2/auc_num)

Train = mutate(Train, median_country_ratio = median_b_a_m/country_num) 
Test = mutate(Test, median_country_ratio = median_b_a_m/country_num)

Train = mutate(Train, ip_device_ratio = ip_num/device_num)
Test = mutate(Test, ip_device_ratio = ip_num/device_num)


Train$log_country_num = log(Train$country_num)
Train$log_ip_num = log(Train$ip_num)
Train$log_device_num = log(Train$device_num+1)
Train$log_median_b_a_m = log(Train$median_b_a_m+1)
Train$log_maxnum_b_a_m = log(Train$maxnum_b_a_m+1)
Train$log_auc_num = log(Train$auc_num) 
Train$min_bid_time = (Train$min_bid_time - mean(Train$min_bid_time))/sd(Train$min_bid_time)
Train$log_total_auc_ratio = log(Train$total_auc_ratio)
Train$log_total_bids_num = log(Train$total_bids_num)

Test$log_country_num = log(Test$country_num)
Test$log_ip_num = log(Test$ip_num)
Test$log_device_num = log(Test$device_num)
Test$log_median_b_a_m = log(Test$median_b_a_m+1)
Test$log_maxnum_b_a_m = log(Test$maxnum_b_a_m+1)
Test$log_auc_num = log(Test$auc_num) 
Test$min_bid_time = (Test$min_bid_time - mean(Test$min_bid_time))/sd(Test$min_bid_time)
Test$log_total_auc_ratio = log(Test$total_auc_ratio)
Test$log_total_bids_num = log(Test$total_bids_num)





Train$outcome = as.factor(Train$outcome)
Train_s_train$outcome = as.factor(Train_s_train$outcome)
Train_s_test$outcome = as.factor(Train_s_test$outcome)

#find the winner of each auction
#find successful bids of each user
#Train$success_bid_num

#find the minium time difference of bids
#Train$min_bid_time
```


#Keeping files
```{r}
write.csv(Train,"MyTrain.csv",row.names=FALSE)
write.csv(Test,"MyTest.csv",row.names=FALSE)
```

#Exploratory Analysis Again
```{r}
library(ggplot2)
ggplot(data = Train, aes(x = country_num)) + 
        geom_histogram(color = "black", fill = "lightblue") # right skewed
ggplot(data = Train, aes(x = ip_num)) + 
        geom_histogram(color = "black", fill = "lightblue") # right skewed
ggplot(data = Train, aes(x = merchandise_num)) + 
        geom_histogram(color = "black", fill = "lightblue") # 1983 of them are 1, 1 of them is 2, discarded
ggplot(data = Train, aes(x = total_bids_num)) + 
        geom_histogram(color = "black", fill = "lightblue", binwidth = 100) +
        xlim(0, quantile(Train$total_bids_num, 0.95)) # right skewed
ggplot(data = Train, aes(x = device_num)) + 
        geom_histogram(color = "black", fill = "lightblue", binwidth = 10) +
        xlim(0,500)# right skewed
ggplot(data = Train, aes(median_b_a_m)) +
        geom_histogram(color = "black", fill = "lightblue", binwidth = 50) +
        xlim(0, quantile(Train$total_bids_num, 0.9)) # right skewed
ggplot(data = Train, aes(maxnum_b_a_m)) +
        geom_histogram(color = "black", fill = "lightblue", binwidth = 5) +
        xlim(0, quantile(Train$maxnum_b_a_m, 0.9)) # right skewed
ggplot(data = Train, aes(auc_num)) +
        geom_histogram(color = "black", fill = "lightblue") # right skewed
ggplot(data = Train, aes(min_bid_time) +
        geom_histogram(color = "black", fill = "lightblue") +
        xlim(0, quantile(Train$min_bid_time, 0.9)) # right skewed
ggplot(data = Train, aes(success_bid_num)) +
        geom_histogram(color = "black", fill = "lightblue", binwidth = 1) +
        xlim(0, quantile(Train$success_bid_num, 0.99)) # right skewed
ggplot(data = Train, aes(total_bids_num)) +
        geom_histogram(color = "black", fill = "lightblue", binwidth = 1) +
        xlim(0, quantile(Train$total_bids_num, 0.99)) # right skewed
ggplot(data = Train, aes(total_auc_ratio)) +
        geom_histogram(color = "black", fill = "lightblue") +
        xlim(0, quantile(Train$total_auc_ratio, 0.99)) # right skewed








ggplot(data = Train, aes(x = median_b_a_m, alpha = 0.5)) + 
        geom_density(aes(fill = outcome)) + 
        xlim(0, quantile(Train$median_b_a_m, 0.9))

ggplot(data = Train, aes(x = max_median_prdt, alpha = 0.5)) + 
        geom_density(aes(fill = outcome)) + 
        xlim(0, quantile(Train$max_median_prdt, 0.9))

ggplot(data = Train, aes(x = success2_auc_ratio, alpha = 0.5)) + 
        geom_density(aes(fill = outcome)) + 
        xlim(0, quantile(Train$success_auc_ratio, 0.9))

ggplot(data = Train, aes(x = median_country_ratio, alpha = 0.5)) + 
        geom_density(aes(fill = outcome)) + 
        xlim(0, quantile(Train$median_country_ratio, 0.9))

ggplot(data = Train, aes(x = device_num, y = outcome, color = outcome)) +
        geom_jitter()

ggplot(data = Train, aes(x = outcome, y = device_num)) +
        geom_boxplot(aes(fill = outcome))

ggplot(data = Train, aes(x = outcome, y = median_b_a_m)) +
        geom_boxplot(aes(fill = outcome))

Train$outcome = as.factor(Train$outcome)

ggplot(data = Train, aes(x = median_b_a_m, y = robot_url_num, color = outcome, alpha=0.5)) +
        geom_jitter()

ggplot(data = Train, aes(x = device_auc_ratio, y = median_ip_ratio, 
                         color = outcome, alpha = 0.5)) + 
        geom_jitter()

ggplot(data = Train, aes(x = max_median_prdt, y = median_device_ratio, 
                         color = outcome, alpha = 0.5)) + 
        geom_jitter()

ggplot(data = Train, aes(x = median_b_a_m, y = auc_num, 
                         color = outcome, alpha = 0.5)) + 
        geom_jitter()
```

#Build Models
##Logistic regression
```{r}
library(ROCR)
logi = glm(outcome ~ robot_url_num, 
           data = Train_s_train, family = "binomial")
PredLogi = predict(logi, newdata = Train_s_test, type = "response")
ROCRpred = prediction(PredLogi, Train_s_test$outcome)
as.numeric(performance(ROCRpred,"auc")@y.values)
```

##Random forest
```{r}
library(randomForest)
library(ROCR)
Train$outcome = as.factor(Train$outcome)
Train_s_train$outcome = as.factor(Train_s_train$outcome)
set.seed(100)
rf_mod1 = randomForest(outcome ~ country_num + ip_num +  
                               device_num + median_b_a_m + maxnum_b_a_m + auc_num +
                               total_bids_num  + total_auc_ratio + max_median_prdt +
                               ip_device_ratio  + ip_auc_ratio +
                               device_auc_ratio + median_auc_ratio + max_auc_ratio + 
                               country_ip_ratio + median_ip_ratio + max_ip_ratio + 
                               country_device_ratio + 
                               median_device_ratio + max_device_ratio,
                       data = Train_s_train, ntree = 10000, importance = TRUE,mtry = 2)
varImpPlot(rf_mod1)
PredRF2 = predict(rf_mod1, newdata = Train_s_test, type = "prob")[,2]
ROCRpredrf = prediction(PredRF2, Train_s_test$outcome)
as.numeric(performance(ROCRpredrf,"auc")@y.values)

# variables: country_num + ip_num +  device_num + median_b_a_m + maxnum_b_a_m + auc_num +
#                               total_bids_num  + total_auc_ratio + max_median_prdt +
#                               success_auc_ratio + success2_auc_ratio +median_country_ratio + 
#                                + ip_device_ratio 
# unused variable:  min_bid_time + success_bid_num + robot_ip_num + robot_url_num
# success_auc_ratio + success2_auc_ratio + success_ip_ratio + success_device_ratio
# + country_auc_ratio + median_country_ratio 

#using cross-validation
library(caret)
library(dplyr)
Yvals = Train$outcome
Yvals = ifelse(Yvals==0, "Human","Robot")
Yvals = as.factor(Yvals)
IndependentVars = select(Train, country_num, ip_num ,  
                               device_num, median_b_a_m, maxnum_b_a_m, auc_num,
                               total_bids_num, total_auc_ratio, max_median_prdt,
                               ip_device_ratio, ip_auc_ratio,
                               device_auc_ratio, median_auc_ratio, max_auc_ratio, 
                               country_ip_ratio, median_ip_ratio, max_ip_ratio, 
                               country_device_ratio, 
                               median_device_ratio, max_device_ratio)
fitControl <- trainControl(method="repeatedcv", number=10, repeats = 5, classProbs = TRUE, summaryFunction = twoClassSummary)
tr = train(IndependentVars, Yvals, method="rf", 
           nodesize=5, ntree=10000, metric="ROC", trControl=fitControl)
#best rf: 0.8918572 with mtry = 2, nodesize = 5, ntree = 10000
#public leader board: 0.88660
predRFCV = predict(tr$finalModel,newdata=Test,type="prob")[,2]


```

##Gradient Boosting Machine
```{r}
library(gbm)
Train$outcome = as.factor(Train$outcome)
gbmmod1 = gbm(outcome ~ country_num + ip_num + total_auc_ratio +
                               total_bids_num + min_bid_time +
                               device_num + median_b_a_m + maxnum_b_a_m +
                               success_bid_num + auc_num + robot_ip_num + robot_url_num, 
              data = Train, dist = "bernoulli", n.tree = 500, shrinkage = 0.005, 
              interaction.depth =5)
predGBM1 = 1 - predict(gbmmod1, newdata = Test, type = "response", n.trees = 500)


#Using cross validation
library(caret)
modelLookup('gbm')

Yvals = as.factor(Train$outcome)
Yvals = ifelse(Yvals==0, "Human","Robot")
Yvals = as.factor(Yvals)
IndependentVars = select(Train, country_num, ip_num, device_num, 
                         median_b_a_m, maxnum_b_a_m, auc_num, min_bid_time,
                         total_auc_ratio, success_bid_num, total_bids_num, 
                         max_median_prdt, success_auc_ratio,
                         success2_auc_ratio, median_country_ratio, ip_device_ratio,
                         robot_ip_num, robot_url_num)
fitControl <- trainControl(method="repeatedcv", number=10, repeats = 3, classProbs = TRUE, summaryFunction = twoClassSummary)
gbmGrid = expand.grid(interaction.depth = c(1,3,5), 
                      n.trees = (4:5)*100, shrinkage = 0.005)
gbmFit = train(IndependentVars, Yvals, method = "gbm", metric="ROC", trControl = fitControl,verbose=FALSE,tuneGrid=gbmGrid)
#best gbm model till now is: 0.9671579 with n.trees=500, interaction.depth=5, shrinkage = 0.005
predGBMCV = predict(gbmFit,newdata=Test,type="prob")[,2]
```

#Neural Networks
```{r}
library(nnet) 
NNmod = nnet(Popular~.,outcome ~ country_num + ip_num + total_bids_num + 
                               device_num + median_b_a_m + maxnum_b_a_m +
                               success_bid_num + auc_num , data = Train,
             size = 5,Hess=FALSE,maxit=2000)
predictNN = predict(NNmod, newdata = Test)
```

#write to file
```{r}
MySubmission = data.frame(bidder_id = Test$bidder_id, prediction = predRFCV) # change prediction
write.csv(rbind(MySubmission, BadTest), "SubmissionRF20-false.csv", row.names=FALSE) # change file name
```



```{r}
sb1 = read.csv("SubmissionRF1.csv")
sb2 = read.csv("SubmissionRF2.csv")
sb3 = read.csv("SubmissionRF3.csv")
sb4 = read.csv("SubmissionRF4.csv")
sb5 = read.csv("SubmissionRF5.csv")
sb6 = read.csv("SubmissionRF6.csv")
sb7 = read.csv("SubmissionRF7.csv")
sb8 = read.csv("SubmissionRF8.csv")
sb9 = read.csv("SubmissionRF9.csv")
sb10 = read.csv("SubmissionPython_RF1.csv")
sb11 = read.csv("SubmissionPython_RF2.csv")
sb12 = read.csv("SubmissionLogi.csv")

sbf1 = read.csv("SubmissionRF17.csv")
sbf2 = read.csv("SubmissionRF18.csv")
sbf3 = read.csv("SubmissionRF19.csv")
sbf4 = read.csv("SubmissionRF20.csv")

#!!!!!!bidder_id inconsistent over sb1 - sb12
pred_avg = (sb7$prediction + sb6$prediction)/2

MySubmission = data.frame(bidder_id = sb6$bidder_id, prediction = pred_avg)
write.csv(MySubmission, "Submission_avg_final.csv",row.names=FALSE)

```

